---
title: "Network-based models"
output: 
  html_document:
    toc: true
    toc_depth: 4
params:
  alpha: 0
  seed: 3
  partition: 0.7
  string_cutoff: 500
  parallel: TRUE
  # type_measure: "C"
  type_measure: "deviance"
  # ---------------------
  folds: 10
  min_degree: 0.3
  s: "lambda.min"
  nlambda: 500
  lambda.min.ratio: 0.001
  limit_xdata: FALSE # FALSE or number of rows
  cores: 5
  # interactive: !r interactive()
  interactive: FALSE
---

```{r}
logger::log_info("yada")
```


```{r, eval=FALSE, include=FALSE}
combine_all <- function(...) {
  dot_args <- rlang::list2(...)  # Capture the named arguments
  # Generate all combinations
  combos <- expand.grid(dot_args, KEEP.OUT.ATTRS = FALSE, stringsAsFactors = FALSE)
  # Convert rows into a list of named lists
  lapply(seq_len(NROW(combos)),function(ix) as.list(setNames(combos[ix, ], names(dot_args))))
}

input_params <- combine_all(
  string_cutoff = 500,
  seed = seq(1, 10, by = 1),
  partition = c(0.7, 0.8),
  type_measure = c("C", "deviance"),
  alpha = c(0)
)


dir.create("Results/reports", showWarnings = FALSE)

purrr::iwalk(input_params, \(x, ix) {
  str_param <- x |> 
    jsonlite::toJSON(auto_unbox = TRUE) |> 
    jsonlite::prettify() |> 
    stringr::str_remove_all("[{}]\n?|(  +)|\"") |> 
    stringr::str_remove("\n$") |> 
    stringr::str_replace_all("\n", " ")
  
  cli::cli_alert_info("Starting ix '{ix}' with '{str_param}'")

  x <- input_params[[ix]]
  suffix <- paste(sort(names(x)), x[sort(names(x))], collapse = "_") |> 
    stringr::str_replace_all(" ", "_")
  file_name <- glue::glue("Results/reports/network_{suffix}.html")
  
  x <- utils::modifyList(list(interactive = FALSE), x)

  cli::cli_alert_info("  Saving to {file_name}")
    
  tryCatch({
    rmarkdown::render("network.Rmd", output_file = file_name, params = x)
  }, error = function(err) {
    logger::log_error("Error with rmarkdown call")
    logger::log_error("str_param {str_param}'")
    if (inherits(err, "condition")) logger::log_error(err$message)
    else logger::log_error(logger::skip_formatter(err))
    lapply(traceback(), \(x) logger::log_error(logger::skip_formatter(x)))
    logger::log_error("End of error message, continuing -----------------------------------")
  })
})
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

cli::start_app()
# Log to console with colors and file without them
logger::log_layout(logger::layout_glue_colors)
logger::log_appender(
  (function(file, append = TRUE, max_lines = Inf, max_bytes = Inf, max_files = 1L) {
    function(lines) {
      if (logger:::needs_stdout()) logger::appender_stdout(lines) else logger::appender_console(lines)
      logger::appender_file(file, append, max_lines, max_bytes, max_files)(cli::ansi_strip(lines))
    }
  })("logger_network.txt")
)

# CLI calls write to logger file
logger::log_appender(logger::appender_file(file = "logger_network.txt"), namespace = "cli")
logger::log_layout(logger::layout_simple, namespace = "cli")
CLI <- structure(400L, level = "CLI", class = c("loglevel", "integer"))
logger::log_threshold(CLI, namespace = "cli")
options(cli.default_handler = function(msg, ..., type = "message") {
  logger::log_level(CLI, cli::default_app()$inline(msg$args$text), namespace = "cli")
  cli:::cli_server_default(msg)
})
```

```{r, eval=FALSE, include=FALSE}
renv::install("sysbiomed/glmSparseNet")
```

##### Load functions to enviroment / init options

```{r}
box::use(
  # Auxiliary functions used often (others use double colon)
  dplyr[select, left_join, mutate, bind_cols],
  logger[log_info, log_warn, log_fatal],
  cli[cli_alert_info, cli_alert_danger, cli_alert_warning, cli_alert_success],
  tictoc[tic, toc],
  survival[Surv],
  prodlim[Hist],
  rlang[`%||%`],
  
  # Custom functons for network operations
  ./Functions/network_utils[
    string_db_homo_sapiens, string_db_local_cache, my_plot, 
    calculate.combined.score_cache, buildStringNetwork_cache, memoise_cache
  ],
  ./Functions/Data_preparation[
    splitTestAndTrain,
  ]
)

# Parallel cv.glmnet
doMC::registerDoMC(cores = params$cores)
cv.glmnet_cache <- memoise::memoise(glmnet::cv.glmnet, cache = memoise_cache)
```

## Read data {.tabset .tabset-fade}

```{r}
.raw_gene <- feather::read_feather("Results/genes_expression.feather")
.raw_surv <- feather::read_feather("Results/survival_data.feather")

# Data structures
data <- list(
  raw = left_join(.raw_surv, .raw_gene, by = "patient")
)

colnames(data$raw) <- data$raw |> colnames() |> stringr::str_replace("[.][0-9]+$", "")
models <- list()
```

```{r, echo=FALSE}
if (!isFALSE(params$limit_xdata)) {
  cat("🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠\n")
  cat("🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠\n")
  cat("🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠\n")
  cat("🟠🟠🟠 XDATA is BEING LIMITED 🟠🟠🟠\n")
  cat("🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠\n")
  cat("🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠\n")
  cat("🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠\n")
  cat("🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠🟠\n")
  data$raw <- data$raw[, seq_len(params$limit_xdata)]
}
```


### Split data

```{r}
set.seed(params$seed)
data$split <- rsample::initial_split(data$raw, prop = params$partition, strata = "vital_status")
data$train <- list(raw = rsample::training(data$split))
data$test <- list(raw = rsample::testing(data$split))
```

```{r, echo=FALSE}
local({
  # Check if data split is the same
  splited <- splitTestAndTrain(.raw_gene, .raw_surv, params$partition, seed_split = params$seed)
  
  stopifnot(
    "Partition is not the same!" = !isFALSE(params$limit_xdata) || all(
      c(
        ydata_train = identical(
          dplyr::tibble(splited$survival_train), 
          dplyr::select(data$train$raw, patient, vital_status, days)
        ),
        xdata_train = identical(
          dplyr::tibble(splited$expression_train), 
          setNames(dplyr::select(data$train$raw, -vital_status, -days), colnames(splited$expression_train))
        ),
        # ---------------------------------------------------------------------------
        ydata_test = identical(
          dplyr::tibble(splited$survival_test), 
          dplyr::select(data$test$raw, patient, vital_status, days)
        ),
        xdata_test = identical(
          dplyr::tibble(splited$expression_test), 
          setNames(dplyr::select(data$test$raw, -vital_status, -days), colnames(splited$expression_test))
        )
      )
    )
  )
})
```


### Build networks

#### Correlation from training data

```{r}
# data$cor <- glmSparseNet:::run.cache(
#   glmSparseNet::networkCorParallel, 
#   xdata = data$train$raw |>
#     dplyr::select(-patient, -vital_status, -days) |> 
#     as.matrix(),
#   n.cores = params$n.cores
# ) |> 
#   abs()
```


#### Build PPI network

```{r ppi_network}
data$ppi <- local({
  local_fun <- memoise::memoise(
    function(cutoff = params$string_cutoff) {
      string_db_homo_sapiens()
      ppi_raw <- string_db_local_cache()
      calculate.combined.score_cache(ppi_raw, score_threshold = cutoff, remove.text = TRUE)
    },
    cache = memoise_cache
  )
  
  ppi_data <- local_fun(params$string_cutoff)
  buildStringNetwork_cache(ppi_data, "ensembl")
})
```

Fill in the blanks of non-existing genes in (filtered) StringDB.

```{r fill_ppi}
data$full_ppi <- local({
  different_names <- colnames(data$raw)[
    !colnames(data$raw) %in% 
      c("patient", "vital_status", "days", colnames(data$ppi))
  ]
  new_size <- length(different_names) + ncol(data$ppi)
  full_ppi <- Matrix::sparseMatrix(
    i = c(), 
    j = c(), 
    x = numeric(0L),
    dims = c(new_size, new_size)
  )
  full_ppi[seq_len(nrow(data$ppi)), seq_len(ncol(data$ppi))] <- data$ppi != 0
  colnames(full_ppi) <- c(colnames(data$ppi), different_names)
  rownames(full_ppi) <- colnames(full_ppi)
  
  gene_names_original <- data$raw |> 
    colnames() |>
    purrr::discard(~.x %in% c("patient", "vital_status", "days"))
  
  # Return original order of data$raw
  full_ppi[gene_names_original, gene_names_original]
})
```


### Prepare `xdata` & `ydata`

```{r prepare_train_data}
data$train$xdata <- data$train$raw |>
  select(-patient, -vital_status, -days) |> 
  as.matrix()

data$train$ydata <- data$train$raw |> 
  select(vital_status, days) |> 
  (\(x) survival::Surv(x$days, x$vital_status))()
```

#### Create folds for k-fold cross-validation

```{r create_folds}
data$train$foldid <- local({
  set.seed(params$seed * 1000 + 331) # slightly differnt seed from original to ensure no conflicts
  folds <- rsample::vfold_cv(data$train$raw, v = params$folds, strata = "vital_status")
  unlist(
    lapply(
      folds$splits,
      \(x) {
        setNames(
          setdiff(seq_len(nrow(data$train$raw)), x$in_id), 
          rep(gsub("Fold", "", x$id) |> as.numeric(), nrow(data$train$raw) - length(x$in_id))
        )
      }
    )
  ) |> 
    sort() |> 
    names() |> 
    as.numeric()
})
```

## Train models

### GLMNET {.tabset .tabset-fade}

#### Training

```{r fit_glment_models}
# Reports only use 1 alpha
glmnet_spec <- local({
  if (params$interactive) {
    list(
      lasso = list(1, "Lasso"), 
      en_0_8 = list(0.8, "Elastic net (0.8)"), 
      en_0_5 = list(0.5, "Elastic net (0.5)")
    )
  } else {
    .id <- switch(
      format(params$alpha),
      "1" = "lasso",
      "0" = "ridge",
      sprintf("en_%s", gsub("[.]", "_", format(params$alpha, scientific = FALSE)))
    )
    
    .label <- switch(
      format(params$alpha),
      "1" = "Lasso",
      "0" = "Ridge",
      sprintf("Elastic Net (%s)", format(params$alpha, scientific = FALSE))
    )
    
    rlang::set_names(list(list(params$alpha,  .label)), .id)
  }
})

glmnet_models <- purrr::map(
  glmnet_spec,
  \(x) {
    x_alpha = x[[1]]
    x_label = x[[2]]
    cli_alert_info("Training model for '{x_label}'...")
    tic()

    new_model <- cv.glmnet_cache(
      data$train$xdata,
      data$train$ydata,
      nlambda = params$nlambda,
      lambda.min.ratio = params$lambda.min.ratio,
      #
      type.measure = params$type_measure %||% "deviance",
      alpha = x_alpha,
      family = "cox",
      parallel = params$parallel,
      foldid = data$train$foldid
    )
    cli_alert_success(
      glue::glue(
        .sep = " ",
        "'{x_label}' model trained in",
        toc(quiet = TRUE)$callback_msg,
        "with",
        sum(coef(models$lasso, s = "lambda.min") != 0),
        "non-zero coefficients"
      )
    )
    attr(new_model, "alpha") <- x_alpha
    attr(new_model, "penalty") <- NULL
    attr(new_model, "covariates") <- colnames(data$train$xdata)
    attr(new_model, "label") <- x_label
    invisible(gc())
    new_model
  }
)
invisible(gc())
```

```{r print_glmnet, echo=FALSE, results='asis'}
purrr::iwalk(glmnet_models, \(.x, .i) {
  cat(glue::glue("\n#### {attributes(.x)$label} { if (.i == names(glmnet_models)[[1]]) '{ .active }' else '' }\n\n"))
  my_plot(.x)
  cat("\n\n")
})
```

```{r assign_models, include=FALSE}
models <- glmnet_models
```


### Network models  {.tabset .tabset-fade}

```{r prepare_data, echo=FALSE}
# Prepares data explicitly

data$covariates <- list(
  orphan = colnames(data$full_ppi),
  orphan_partial = intersect(colnames(data$ppi), colnames(data$raw)),
  hub = colnames(data$full_ppi),
  hub_partial = intersect(colnames(data$ppi), colnames(data$raw))
)

data$penalty <- local({
  calc_penalty <- \(x, fun, min_degree = params$min_degree) fun(Matrix::colSums(x) + Matrix::rowSums(x)) + min_degree
 
  partial_covariates <- data$covariates$orphan_partial
  list(
    orphan = calc_penalty(data$full_ppi, glmSparseNet::orphanHeuristic),
    orphan_partial = calc_penalty(data$full_ppi[partial_covariates, partial_covariates], glmSparseNet::orphanHeuristic),
    hub = calc_penalty(data$full_ppi, glmSparseNet::hubHeuristic),
    hub_partial = calc_penalty(data$full_ppi[partial_covariates, partial_covariates], glmSparseNet::hubHeuristic)
  )
})
```

#### Train models

```{r network_models}
# Network-based models training

new_models <- purrr::map(
  rlang::set_names(c("hub", "hub_partial", "orphan", "orphan_partial")),
  \(ix) {
    x_label <- gsub("_", " ", ix) |> 
      tools::toTitleCase() |> 
      stringr::str_replace("Partial", "(partial)")
    
    cli_alert_info("Training model for '{ix}'...")
    tic()
    new_model <- cv.glmnet_cache(
      data$train$xdata[, data$covariates[[ix]]],
      data$train$ydata,
      penalty = data$penalty[[ix]],
      alpha = params$alpha,
      nlambda = params$nlambda,
      lambda.min.ratio = params$lambda.min.ratio,
      type.measure = params$type_measure %||% "deviance",
      family = "cox",
      foldid = data$train$foldid,
      parallel = params$parallel
    )
    invisible(gc())
    attr(new_model, "alpha") <- params$alpha
    attr(new_model, "penalty") <- data$penalty[[ix]]
    attr(new_model, "covariates") <- data$covariates[[ix]]
    attr(new_model, "label") <- x_label
    
    cli_alert_success(
      "'{x_label}' model trained in {toc(quiet = TRUE)$callback_msg} with {sum(coef(new_model, s = 'lambda.min') != 0)} non-zero coefficients"
    )
    
    new_model
  }
)

models <- Reduce(
  x = names(new_models),
  f = \(u, x) {
    u[[x]] <- new_models[[x]]
    u
  },
  init = models
)
```

#### Penalty's histogram

```{r, echo=FALSE}
penalty_plot_data <- data$penalty |> 
  purrr::imap(\(x, i) tibble::tibble(penalty = x, network = i)) |> 
  purrr::list_rbind()
```

```{r penalty_histogram, echo = FALSE, warning=FALSE}
penalty_plot_data |> 
  ggplot2::ggplot() +
  ggplot2::geom_histogram(
    ggplot2::aes(x = penalty, fill = network), 
    binwidth = .5, 
    alpha = 0.5, 
    na.rm = TRUE
  ) +
  ggplot2::scale_y_continuous(trans = "log10") +
  ggplot2::ylab("(log10)") +
  ggplot2::facet_wrap(~network) +
  ggplot2::theme_minimal()
```

#### Penalty's density

```{r penalty_density_plot, echo=FALSE}
penalty_plot_data |> 
  ggplot2::ggplot() +
  ggplot2::geom_density(ggplot2::aes(x = penalty, fill = network), alpha = 0.5, kernel = "rectangular") +
  ggplot2::scale_x_continuous(trans = "log10") +
  ggplot2::xlab("penalty (log10)") +
  ggplot2::facet_grid(cols = ggplot2::vars(network), scales = "free") + 
  ggplot2::theme_minimal()
```

```{r plot_network, results='asis'}
purrr::iwalk(new_models, \(.x, .i) {
  cat(glue::glue("\n#### {attributes(.x)$label} {if (.i == names(new_models)[[1]]) '{ .active }' else  ''}\n\n"))
  my_plot(.x)
  cat("\n\n")
})
```


## Test  {.tabset .tabset-fade}

- C-Index
- Log-Rank test
- IBS

```{r test_prepare}
data$test$xdata <- data$test$raw |>
  dplyr::select(-patient, -vital_status, -days) |> 
  as.matrix()

data$test$ydata <- data$test$raw |> 
  dplyr::select(vital_status, days) |> 
  (\(x) survival::Surv(x$days, x$vital_status))()
```

### Calculate metrics

```{r test_calc_metrics}
results_l <- lapply(
  rlang::set_names(names(models)),
  \(x) {
    fit <- models[[x]]
    
    if (!any(coef(fit, s = "lambda.min") != 0)) {
      return(
        tibble::tibble(
          model = x, 
          label = attr(fit, "label"), 
          c_index = NA, 
          log_rank_pvalue = NA,
          ibs = NA
        )
      )
    }
    
    # C-Index -----------------------------------------------------------------
    covariates <- attr(fit, "covariates")
    prob_test <- stats::predict(fit, newx = data$test$xdata[, covariates], s = "lambda.min", type = "response")
    c_index <- survival::concordance(data$test$ydata ~ prob_test, reverse=TRUE)$concordance
    
    risk_scores <- stats::predict(fit, newx = data$test$xdata[, covariates], s = "lambda.min", type = "link")
    risk_group <- ifelse(risk_scores > median(risk_scores), "High", "Low")
    
    # Log-Rank ----------------------------------------------------------------
    
    log_rank_result <- if (length(unique(risk_group)) == 2L) {
      survival::survdiff(data$test$ydata ~ risk_group) 
    } else {
      list(pvalue = NA)
    }

    # IBS ---------------------------------------------------------------------
    
    fit_coef <- coef(fit, s = "lambda.min") |> 
      magrittr::extract(TRUE, 1) |> 
      purrr::discard(~.x == 0)
    
    ibs_value <- tryCatch({
      local_data <- bind_cols(
        data$test$ydata,
        data$test$xdata[, names(fit_coef)]
      )
     
      if (length(fit_coef) <= 1000) {
        fit_coxph <- survival::coxph(
          formula = Surv(time, status) ~ .,
          data = local_data,
          init = fit_coef,
          iter.max = 0,
          x = TRUE
        )  
        
        ibs_result <- pec::pec(
          object = list("Cox" = fit_coxph),
          formula = Surv(time, status) ~ 1,
          data = local_data,
          times = sort(unique(local_data$time)), # time points for evaluation
          start = min(local_data$time),
          maxtime = max(local_data$time)
        )
        pec::crps(ibs_result)[2]
      } else {
        NA
      }
    }, error = function(err) NA)
        
    # Result ------------------------------------------------------------------
    
    tibble::tibble(
      model = x, 
      label = attr(fit, "label"), 
      nzeros = length(fit_coef),
      c_index = c_index, 
      log_rank_pvalue = log_rank_result$pvalue,
      ibs = ibs_value
    )
  }
)
results <- purrr::list_rbind(results_l)
  
```
### 👑 Results {.active}

```{r test_results, echo=FALSE}
results |> knitr::kable()
```

### C-Index vs. Log-Rank test

```{r test_cindex_log_rank, echo=FALSE}
results |> 
  dplyr::mutate(label = sprintf("%s\n(p: %.3f, c: %.3f)", label, log_rank_pvalue, c_index)) |>
  ggplot2::ggplot(ggplot2::aes(x = c_index, y = log_rank_pvalue, label = label)) +
  ggrepel::geom_text_repel(min.segment.length = .2, segment.color = "gray") + 
  ggplot2::geom_point(color = "purple") +
  ggplot2::xlim(0,1) + 
  ggplot2::ylim(0, 1) +
  ggplot2::xlab("C-Index") +
  ggplot2::ylab("Log-rank p-value") +
  ggplot2::geom_hline(yintercept = 0.05, linetype = "dashed", color = "red", alpha = .4) +
  ggplot2::annotate("text", x = 0, y = 0.045, label = "p-value ≤ 0.05", hjust = 0, vjust = 1, color = "red", alpha = .4) +
  ggplot2::theme_minimal()
```

### C-Index vs. IBS

```{r test_cindex_ibs, echo=FALSE}
results |> 
  dplyr::mutate(label = sprintf("%s\n(ibs: %.3f, cix: %.3f)", label, ibs, c_index)) |>
  ggplot2::ggplot(ggplot2::aes(x = c_index, y = ibs, label = label)) +
  ggrepel::geom_text_repel(min.segment.length = .2, segment.color = "gray", max.overlaps = 20) + 
  ggplot2::geom_point(color = "purple") +
  ggplot2::xlab("C-Index") +
  ggplot2::ylab("IBS") +
  ggplot2::theme_minimal()
```

```{r test_km, echo=FALSE}
km_result <- purrr::map(
  rlang::set_names(names(models)),
  \(x) {
    fit <- models[[x]]
  
    if (!any(coef(fit, s = "lambda.min") != 0)) return(NULL)

    covariates <- attr(fit, "covariates")
    
    risk_scores <- stats::predict(fit, newx = data$test$xdata[, covariates], s = "lambda.min", type = "link")
    risk_group <- ifelse(risk_scores > median(risk_scores), "High", "Low")
    
    if (length(unique(risk_group)) == 2L) {
      local_data <- select(data$test$raw, time = "days", status = "vital_status") |> 
        mutate(risk_group = risk_group)
      surv_fit <- survival::survfit(survival::Surv(time, status) ~ risk_group, data = local_data)
      survminer::ggsurvplot(
        surv_fit, 
        data = local_data,
        pval = TRUE,                 # Add log-rank test p-value
        conf.int = TRUE,             # Add confidence intervals
        risk.table = TRUE,           # Add risk table below the plot
        palette = c("#E7B800", "#2E9FDF"), # Customize colors
        xlab = "Time (days)", 
        ylab = "Survival Probability",
        legend.title = "Risk",
        legend.labs = c("High", "Low"), # Customize legend labels
        ggtheme = ggplot2::theme_minimal()          # Use a minimal theme
      )
    }
  }
)
```

### KM {.tabset .tabset-fade}

```{r test_km_plot, echo=FALSE, results='asis'}
for (x in names(km_result)) {
  if (is.null(km_result[[x]])) next
  cat("#### ", x, "\n\n")
  print(km_result[[x]])
  cat("\n\n")
}
```

## All {.tabset .tabset-fade}

```{r all_prepare}
data$all <- list(
  xdata = data$raw |>
    dplyr::select(-patient, -vital_status, -days) |> 
    as.matrix(),
  ydata = data$raw |> 
    dplyr::select(vital_status, days) |> 
    (\(x) survival::Surv(x$days, x$vital_status))()  
)
```

### Calculate results

```{r all_calculate_metrics}
results_all <- purrr::map(
  rlang::set_names(names(models)),
  \(x) {
    fit <- models[[x]]
    
    if (!any(coef(fit, s = "lambda.min") != 0)) {
      return(
        tibble::tibble(
          model = x, 
          label = attr(fit, "label"), 
          c_index = NA, 
          log_rank_pvalue = NA,
          ibs = NA
        )
      )
    }
    
    # C-Index -----------------------------------------------------------------
    
    covariates <- attr(fit, "covariates")
    prob_test <- stats::predict(fit, newx = data$all$xdata[, covariates], s = "lambda.min", type = "response")
    c_index <- survival::concordance(data$all$ydata ~ prob_test, reverse=TRUE)$concordance
    
    # Log-rank ----------------------------------------------------------------
    
    risk_scores <- stats::predict(fit, newx = data$all$xdata[, covariates], s = "lambda.min", type = "link")
    risk_group <- ifelse(risk_scores > median(risk_scores), "High", "Low")
    
    log_rank_result <- if (length(unique(risk_group)) == 2L) {
      survival::survdiff(data$all$ydata ~ risk_group) 
    } else {
      list(pvalue = 1)
    }
    
    # IBS ---------------------------------------------------------------------
    
    fit_coef <- coef(fit, s = "lambda.min") |> 
      magrittr::extract(TRUE, 1) |> 
      purrr::discard(~.x == 0)
    
    ibs_value <- tryCatch({
      local_data <- bind_cols(
        data$all$ydata,
        data$all$xdata[, names(fit_coef)]
      )
  
      if (length(fit_coef) <= 1000) {
        fit_coxph <- survival::coxph(
          formula = Surv(time, status) ~ .,
          data = local_data[,1:5000],
          init = fit_coef[1:4998],
          iter.max = 0,
          x = TRUE
        )
    
        ibs_result <- pec::pec(
          object = list("Cox" = fit_coxph),
          formula = Surv(time, status) ~ 1,
          data = local_data,
          times = sort(unique(local_data$time)), # time points for evaluation
          start = min(local_data$time),
          maxtime = max(local_data$time)
        )
        
        pec::crps(ibs_result)[2]
      } else {
        NA
      }
    }, error = function(errr) NA)
    
    # Result ------------------------------------------------------------------
    
    tibble::tibble(
      model = x,
      label = attr(fit, "label"),
      c_index = c_index,
      log_rank_pvalue = log_rank_result$pvalue,
      ibs = ibs_value
    )
  }
) |> 
  purrr::list_rbind()
```

### Results {.active}

```{r all_results_table, echo=FALSE}
results_all |> knitr::kable()
```


### C-Index vs. Log-Rank test

```{r all_cindex_log_rank, echo=FALSE}
results_all |> 
  dplyr::mutate(label = sprintf("%s\n(p: %.2g, c: %.3f)", label, log_rank_pvalue, c_index)) |>
  ggplot2::ggplot(ggplot2::aes(x = c_index, y = log_rank_pvalue, label = label)) +
  ggrepel::geom_text_repel(min.segment.length = .2, segment.color = "gray") + 
  ggplot2::geom_point(color = "purple") +
  # ggplot2::xlim(0, 1) + 
  # ggplot2::ylim(0, 1) +
  ggplot2::xlab("C-Index") +
  ggplot2::ylab("Log-rank p-value") +
  ggplot2::geom_hline(yintercept = 0.05, linetype = "dashed", color = "red", alpha = .4) +
  ggplot2::annotate("text", x = 0, y = 0.045, label = "p-value ≤ 0.05", hjust = 0, vjust = 1, color = "red", alpha = .4) +
  ggplot2::theme_minimal()
```

### C-Index vs. IBS

```{r all_cindex_ibs, echo=FALSE}
results_all |> 
  dplyr::mutate(label = sprintf("%s\n(ibs: %.2g, cix: %.3f)", label, ibs, c_index)) |>
  ggplot2::ggplot(ggplot2::aes(x = c_index, y = ibs, label = label)) +
  ggrepel::geom_text_repel(min.segment.length = .2, segment.color = "gray") + 
  ggplot2::geom_point(color = "purple") +
  # ggplot2::xlim(0, 1) + 
  # ggplot2::ylim(0, 1) +
  ggplot2::xlab("C-Index") +
  ggplot2::ylab("Log-rank p-value") +
  ggplot2::geom_hline(yintercept = 0.05, linetype = "dashed", color = "red", alpha = .4) +
  ggplot2::annotate("text", x = 0, y = 0.045, label = "p-value ≤ 0.05", hjust = 0, vjust = 1, color = "red", alpha = .4) +
  ggplot2::theme_minimal()
```


```{r all_km, echo=FALSE}
km_result_all <- purrr::map(
  rlang::set_names(names(models)),
  \(x) {
    fit <- models[[x]]
    
    if (!any(coef(fit, s = "lambda.min") != 0)) {
      return(NULL)
    }

    covariates <- attr(fit, "covariates")
    
    risk_scores <- stats::predict(fit, newx = data$all$xdata[, covariates], s = "lambda.min", type = "link")
    risk_group <- ifelse(risk_scores > median(risk_scores), "High", "Low")
    
    if (length(unique(risk_group)) == 2L) {
      local_data <- select(data$raw, time = "days", status = "vital_status") |> 
        mutate(risk_group = risk_group)
      surv_fit <- survival::survfit(survival::Surv(time, status) ~ risk_group, data = local_data)
      survminer::ggsurvplot(
        surv_fit, 
        data = local_data,
        pval = TRUE,                 # Add log-rank test p-value
        conf.int = TRUE,             # Add confidence intervals
        risk.table = TRUE,           # Add risk table below the plot
        palette = c("#E7B800", "#2E9FDF"), # Customize colors
        xlab = "Time (days)", 
        ylab = "Survival Probability",
        legend.title = "Risk",
        legend.labs = c("High", "Low"), # Customize legend labels
        ggtheme = ggplot2::theme_minimal()          # Use a minimal theme
      )
    }
  }
)
```

### KM {.tabset .tabset-fade}

```{r all_km_plot, echo=FALSE, results='asis'}
for (x in names(km_result_all)) {
  if (is.null(km_result_all[[x]])) next
  cat("#### ", x, "\n\n")
  print(km_result_all[[x]])
  cat("\n\n")
}
```


## Saving results

```{r saving_test_results, echo=FALSE}
local({
  param_hash <- substr(rlang::hash(params[!names(params) %in% "seed"]), 1, 6)
  file_name <- sprintf("results_h%s_s%d.Rdata", param_hash, params$seed)
  full_path <- here::here("Results", "network_table", file_name)
  
  dir.create(dirname(full_path), showWarnings = FALSE)
  e = new.env()
  e$params <- params[!names(params) %in% c("parallel", "cores")]
  e$results <- results
  e$results_all <- results_all
  
  e$coefs <- purrr::map(models, \(.x) {
    coef_list <- coef(.x, s = "lambda.min")
    rownames(coef_list)[coef_list[, 1] != 0]
  })
  
  save(list = ls(e), envir = e, file = full_path)
  cli_alert_success("Results saved to {full_path}")
  invisible(NULL)
})
```










